Kernel Smoothing And Heat Equation

### 2020-11-18 latex/draft.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb} 
\usepackage{soul}
\usepackage{ulem}

@@

\begin{itemize}
% 11/10/2020  
\item 11/10/2020. We implemented circular smoother on both fixed bandwidth and adaptive bandwidth scenarios; and did the corresponding simulation. We noticed for the circular data, the adaptive bandwidth cannot beat the optimal fixed bandwidth. Fixed bandwidth achieve the smallest MSE in our $y=\sin(x)$ setting. We also noticed the circular smoother performs better than Euclidean smoother in the circular data ($y=\sin(x)$). 
\begin{verbatim}
           euclidean   circular
Adaptive  0.19821445 0.19821445
logb=-3   1.00313133 1.00313133
logb=-2.4 1.00313133 1.00313133
logb=-1.8 1.00313133 1.00313133
logb=-1.2 0.11346202 0.11227971
logb=-0.6 0.02875581 0.02717735
logb=0    0.08004308 0.08145240
logb=0.6  0.44585526 0.52684029
logb=1.2  0.49326980 0.50454607
logb=1.8  0.50018979 0.50094139
logb=2.4  0.50068896 0.50068896
logb=3    0.50068896 0.50068896
\end{verbatim}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb} 
\usepackage{soul}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{grffile} % allow use .eps files
\usepackage{float}

@@

\begin{itemize}
% 12/01/2020  
\item 12/01/2020. 
\begin{figure}[H]
\includegraphics[width=\linewidth]{pic/sim.plot1.eps}
\includegraphics[width=\linewidth]{pic/sim.plot2.eps}
\includegraphics[width=\linewidth]{pic/sim.plot3.eps}
\end{figure}

% 11/17/2020  
\item 11/17/2020.

TODOLIST:
\begin{enumerate}
\item Editor: Emacs, Vim
\item Learn: Command line, \texttt{ssh}, \texttt{zsh},\texttt{bash}, to remotely control.
\item \texttt{.eps} $\rightarrow$ \texttt{.eps}; change \texttt{postscript()} to \texttt{pdf(), png(), tiff()}
\item Residual trend means under-smoothing (overfitting)
\item manually compute the 2 extreme points (second order taylor expansion) -- empirical MSE and theoretical MSE
\end{enumerate}

% 11/10/2020  
\item 11/10/2020. We implemented circular smoother on both fixed bandwidth and adaptive bandwidth scenarios; and did the corresponding simulation. We noticed for the circular data, the adaptive bandwidth cannot beat the optimal fixed bandwidth. Fixed bandwidth achieve the smallest MSE in our $y=\sin(x)$ setting. We also noticed the circular smoother performs better than Euclidean smoother in the circular data ($y=\sin(x)$).

\begin{verbatim}
           euclidean   circular
Adaptive  0.19821445 0.19821445
logb=-3   1.00313133 1.00313133
logb=-2.4 1.00313133 1.00313133
logb=-1.8 1.00313133 1.00313133
logb=-1.2 0.11346202 0.11227971
logb=-0.6 0.02875581 0.02717735
logb=0    0.08004308 0.08145240
logb=0.6  0.44585526 0.52684029
logb=1.2  0.49326980 0.50454607
logb=1.8  0.50018979 0.50094139
logb=2.4  0.50068896 0.50068896
logb=3    0.50068896 0.50068896
\end{verbatim}
